Hydras \& Co.

### 2022-02-18 doc/part-hydras.tex
making gaia's T1 an instance of ON (doc)

\chapter{Introduction to ordinal numbers and ordinal notations}

@@

>>>>

\chapter{Introduction to ordinal numbers and ordinal notations}
\label{chap:ON}

@@

\section{Ordinal Notations and \gaia's ordinals}
Module~\href{../theories/html/gaia.T1Bridge.html}{gaia.T1Bridge} contains an instance of class \texttt{ON E0lt compare}, where \texttt{E0lt} is the order on the well-formed ordinal terms below $\epsilon_0$ defined in \gaia library (please see Chapter~\ref{gaia-chapter}).
